\keys{Software Testing Process Improvement, DevOps, Agile Frameworks, MPT.Br}

\begin{abstract}{FreeTest Framework - A Framework for Improvement of the Software Testing Process in midsized brazilian companies and startups}

The Information Technology market (T.I.) is growing. In the information age, world economies have been investing more and more in the services market. Within this competitive scenario, software testing is an important component for raising the quality of software developed in Brazil and its global competitiveness. However, Micro and Small Enterprises (MPEs) and startups have limited resources for investments in software testing maturity processes, tools and models in their business. In view of this, this work has as general proposal to produce an apparatus for improvement of software testing process for MPEs and startups. Within this apparatus, a generic and generic generic test process model was created, containing list of specific practices, maturity levels and list of supporting tools. To facilitate the deployment of the test process, a deployment guide was created to assist MPEs and startups in deploying the test process. This deployment guide will act as a deployment wizard (online), which, based on a series of questions, will help the company to implement the process in the best possible way, from the point of view of its Level of maturity and support tools that the process supports.

The defined testing process has been redesigned based on the old FreeTest Method testing process, in this case now, containing process areas, specific activities and tools that are aligned to the ecosystem of MSEs and startups. The focus of this new process was to insert activities that could be automated, since they were well-accepted activities by the MSEs, since in their context, the technical team is usually formed by a large majority of developers and a small portion by testers, facilitating So the entry of automated mechanisms to carry out activities focusing on the quality of the code. Finally, the implementation guide and the process framework have been made available on a web platform and will be used to facilitate the implementation and maintenance of the process.

\end{abstract}
